### 2021-12-08 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@2aaa3526e1b06bdd5e6e0e7bf95b506fee905cc5 🚀

Note that when \(s=0\), \(\mathbf{Tr}(\mathbf{M}) = 0\) (the classifier
is \emph{always} wrong), when \(s=0.5\), the classifier is no-skill and
guesses at random, and when \(s=1\), the classifier is perfect.

>>>>

Note that when \(s=0\), \(\text{Tr}(\mathbf{M}) = 0\) (the classifier is
\emph{always} wrong), when \(s=0.5\), the classifier is no-skill and
guesses at random, and when \(s=1\), the classifier is perfect.
